Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check section on one body densities

        \subsubsection{One-Body Densities}
            We now look at one-body densities for the value of $\alpha$ found in
            \autoref{eq:optimal_interacting_alpha}. The results for a system consisting
            of $n=100$ particles are displayed in \autoref{fig:one_body_density_100}.
            In this figure we see the densities for for a system confined to a
            perturbed elliptic trap with and without interaction. We see that for the
            interacting case, the one-body density is skewed towards a larger
            $\abs{\vf{r}}$, as is expected. The "ideal" density, a system with spherical
            trap, is also included in the figure.

>>>>

        \subsubsection{One-Body Densities}
            We now look at one-body densities for the value of $\alpha$ found in
            \autoref{eq:optimal_interacting_alpha}. The results for a system
            consisting of $N=100$ particles are displayed in
            \autoref{fig:one_body_density_100}.  In this figure we see the
            densities for a system confined to a perturbed elliptic trap with
            and without interaction. We see that for the interacting case, the
            one-body density is skewed towards a larger $\abs{\vf{r}}$, as is
            expected. The hard core prevents the bosons from stacking on top of
            each other spatially. By increasing the hard core radius this trend
            will be more noticeable. The one-body density of the "ideal" system
            is also included in the figure.
